Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-19 outputs/paper/paper.Rmd
ggplot

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
```
* number of survey participants of age in the range of 20~40 is unexpectedly low -> not many people in ages between 20-40 participated in the survey
* Clinton's vote is higher than trump's vote in this survey, which contradicts the election result of 2016, reader should keep in mind that this survey is more biased towards clinton.

@@

```{r, echo=FALSE}
reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

reduced_data$Immigration <- factor(reduced_data$Immigration, levels = c("Strongly disagree","Disagree", "Neither","Agree","Strongly agree"))

@@

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's Vote Choice of 2016 Presidential Election",
       caption = "Figure 3: Distribution of survey respondents' vote choice") +
  theme(legend.position = "none")

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Governemnt Spending Enough to Improve Conditions of Black Population?",
       caption = "Figure 4: Opinion on National Spending on Improving Conditions of Black Population") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's Vote Choice of 2016 Presidential Election by Brith Place",
       caption = "Figure 5: Distribution of survey respondents' vote choice by birth place",
       fil = "Candidate")

@@

reduced_data %>%
  drop_na(nation_welfare) %>%
  ggplot(aes(x = race, fill = nation_welfare)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Government Spending Enough on Welfare?",
       caption = "Figure 6: Opinion on National Spending on welfare") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())
```

@@

reduced_data %>%
  ggplot(aes(x = nation_race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = social_security, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(Family_income, 
                                       levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999",
                                                  "$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar() +
  labs(fill = "Family Income") +
  coord_flip()

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip()

>>>>

# Data
```{r, include=FALSE, echo=FALSE}
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

reduced_data$Immigration <- factor(reduced_data$Immigration, levels = c("Strongly disagree","Disagree", "Neither","Agree","Strongly agree"))
```
* number of survey participants of age in the range of 20~40 is unexpectedly low -> not many people in ages between 20-40 participated in the survey
* Clinton's vote is higher than trump's vote in this survey, which contradicts the election result of 2016, reader should keep in mind that this survey is more biased towards clinton.

@@

```{r, echo=FALSE}

@@

reduced_data %>%
  ggplot(aes(x = gender, fill = gender)) +
  geom_bar() +
  #scale_fill_manual("gender", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Gender",
       caption = "Figure 3: Distribution of survey respondents' gender") +
  theme(legend.position = "none")

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's Vote Choice of 2016 Presidential Election",
       caption = "Figure 4: Distribution of survey respondents' vote choice") +
  theme(legend.position = "none")

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Spending Enough to Improve Conditions of Black Population?",
       caption = "Figure 5: Opinion on National Spending on Improving Conditions of Black Population") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's Vote Choice of 2016 Presidential Election by Brith Place",
       caption = "Figure 6: Distribution of survey respondents' vote choice by birth place",
       fil = "Candidate")

@@

reduced_data %>%
  drop_na(nation_welfare) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_welfare)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Spending Enough on Welfare?",
       caption = "Figure 7: Opinion on National Spending on welfare") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

reduced_data %>%
  ggplot(aes(x = degree, fill = factor(Family_income, 
                                       levels = c("$170,000 or over","$130,000 ~ $169,999","$90,000 ~ $129,999","$60,000 ~ $89,999",
                                                  "$40,000 ~ $59,999","$20,000 ~ $39,999","$10,000 ~ $19,999","Under $10,000")))) +
  geom_bar(position = "dodge") +
  labs(fill = "Family Income") +
  coord_flip()
```

@@

# reduced_data %>%
#   ggplot(aes(x = nation_race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

@@

# reduced_data %>%
#   ggplot(aes(x = social_security, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

# reduced_data %>%
#   ggplot(aes(x = race, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

reduced_data %>%
  ggplot(aes(x = Immigration, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip() +
  facet_wrap(~born_US)
